I don't know if projection is categorical. \\ Did \citealt{mandelkern-etal2020} discover that it is?

### 2023-12-20 output/naturalness-paper/paper.tex
fixed modeling stuff

These observations were confirmed by a posthoc pairwise comparison of the naturalness ratings of the contents associated with the six controls and 20 target expressions in the explicit ignorance context using the `emmeans' package (\citealt{emmeans}) in R (\citealt{r}). The input to the pairwise comparison was a Bayesian mixed-effects beta regression model with weakly informative priors that was fitted using the `brms' package (\citealt{buerkner2017}). The model predicted naturalness ratings\footnote{To model the ratings using a beta regression, the ratings were first transformed from the interval [0,1] to the interval (0,1) using the method proposed in \citealt{smithson-verkuilen2006}.} from a fixed effect of expression (with treatment coding and `continue' as reference level) and included random by-participant and by-item intercepts (where an item is a complement clause). The output of the pairwise comparison were 95\% highest density intervals (hdis) of estimated marginal mean differences between each of the 26 contents. We assume that two contents differ in their naturalness in the explicit ignorance context if their hdi does not include 0.

As shown in Table \ref{t:pairwise},\footnote{Even though the naturalness ratings collected from the participants range from 0 to 1, the estimated marginal mean differences represented in this table range from -2.7 (difference between the pre-state content of {\em continue} and the CC of {\em say} to 2.7 (difference between the CC of {\em say} and the prejacent of {\em too}). These large estimated marginal mean differences are possible because they are based on the estimates and 95\% credible intervals of the  contents associated with the 26 expressions, where the estimates ranged from -1.32 (for the intercept, which was {\em continue}) to 2.69 (for {\em say}). The full model output is available here: \url{LINK TO TABLE IN REPO} {\bf ADD THIS AFTER FINALIZING SCRIPTS}.} the pairwise comparison suggests differences between the naturalness ratings of the CCs of the five factive predicates: The ratings of {\em be annoyed} are lower than those of {\em know}, which in turn are lower than those of {\em see} and {\em discover}, which in turn are lower than those of {\em reveal}. There is also variation between the factive predicates and the presuppositional controls: While all five factive predicates are more natural in explicit ignorance contexts than {\em continue, too} and {\em also}, {\em know} is additionally more natural than {\em again} and {\em stop}, and {\em see, discover} and {\em reveal} are additionally more natural than the {\em it-}cleft. Finally, the naturalness ratings in explicit ignorance contexts for {\em see} and {\em discover} do not differ from those of the nonfactives {\em confess, inform}, and {\em acknowledge}, and those of {\em reveal} do not differ from those of the nonfactives {\em admit, hear}, and {\em prove}. These results suggest that naturalness ratings in explicit ignorance contexts do not provide empirical support for categorical projection or for a categorical distinction between factive and nonfactive predicates.

\begin{table}[!h]
\addtolength{\tabcolsep}{-.19em}
\centering
\begin{tabular}{r | cccccccccccccccccccccccccc}
& \rots{\bf continue} & \rots{\bf too} & \rots{\bf also} & \rots{\bf again} & \rots{\bf stop} & \rots{\color{orange}{\bf be annoyed}\color{black}} & \rots{\bf cleft} & \rots{\color{orange}{\bf know}\color{black}} & \rots{\color{green}{\bf demonstrate}\color{black}} & \rots{\color{green}{\bf pretend}\color{black}} & \rots{\color{green}{\bf inform}\color{black}} & \rots{\color{green}{\bf confess}\color{black}} & \rots{\color{orange}{\bf see}\color{black}} & \rots{\color{green}{\bf acknowledge}\color{black}} & \rots{\color{orange}{\bf discover}\color{black}} & \rots{\color{green}{\bf admit}\color{black}} & \rots{\color{green}{\bf hear}\color{black}} & \rots{\color{green}{\bf prove}\color{black}} & \rots{\color{orange}{\bf reveal}\color{black}} & \rots{\color{green}{\bf announce}\color{black}} & \rots{\color{green}{\bf be right}\color{black}} & \rots{\color{green}{\bf establish}\color{black}} & \rots{\color{green}{\bf confirm}\color{black}} & \rots{\color{green}{\bf suggest}\color{black}} & \rots{\color{green}{\bf think}\color{black}} & \rots{\color{green}{\bf say}\color{black}} \\
\hline
\input{../../results/main/models/analysis1/table1}
\hline
\end{tabular}
\caption{Estimated marginal mean differences between the 26 target and control contents in the explicit ignorance context by expression, with expressions ordered by mean naturalness rating in that context. The color coding indicates whether the difference between the naturalness ratings for contents of the expressions in the first column and those of the expressions in the top row was positive or negative, as well as the size of the difference. A white cell means that there was no difference.\\
Positive difference: \colorbox{purple1}{\makebox[4em][c]{$>=1.5$}}, \colorbox{purple2}{\makebox[4em][c]{($1.5,0.5]$}}, 
\colorbox{purple3}{\makebox[4em][c]{($0.5, 0]$}} \\
Negative difference: \colorbox{yellow1}{\makebox[4em][c]{$>=-1.5$}}, \colorbox{yellow2}{\makebox[4em][c]{($-1.5, -0.5]$}}, \colorbox{yellow3}{\makebox[4em][c]{($-0.5, 0]$}} 
}\label{t:pairwise}
\end{table}

@@

These observations were confirmed by posthoc pairwise comparisons of the naturalness ratings in the three contexts for each of the 20 predicates, again using the `emmeans' package (\citealt{emmeans}). The input to the pairwise comparisons were 20 Bayesian mixed-effects beta regression models with weakly informative priors that were fitted using the `brms' package (\citealt{buerkner2017}). The models predicted, for each predicate, the naturalness ratings\footnote{As in the model reported above, the ratings were transformed to the interval (0,1).} from a fixed effect of context (with treatment coding and `explicit ignorance' as reference level) and included random by-item intercepts. The output of the pairwise comparison are 95\% hdis of estimated marginal mean differences between each of the three contexts for each of the 20 contents. We assume that the naturalness ratings between two contexts differ if their hdi does not include 0.\footnote{The full model output is available here: \url{LINK TO TABLE IN REPO}.{\bf ADD AFTER FINALIZING SCRIPTS}} As shown in Fig.~\ref{fig:acc-by-context}, naturalness ratings in explicit ignorance vs.\ lower or higher prior probability contexts do not provide support for a categorical distinction between presuppositions and nonpresuppositions.

>>>>

These observations were confirmed by a posthoc pairwise comparison of the estimated means for each control and target expression in the explicit ignorance context using the `emmeans' package (\citealt{emmeans}) in R (\citealt{r}). The input to the pairwise comparison was a Bayesian mixed-effects beta regression model with weakly informative priors that was fit using the `brms' package (\citealt{buerkner2017}). The model predicted naturalness ratings\footnote{To model the ratings using a beta regression, the ratings were first transformed from the interval [0,1] to the interval (0,1) using the method proposed in \citealt{smithson-verkuilen2006}.} from a fixed effect of expression (with treatment coding and `continue' as reference level) and included random by-participant and by-item intercepts (where an item is a complement clause). The output of the pairwise comparison were 95\% highest density intervals (HDIs) of estimated marginal mean differences between each of the expressions. We assume that two expressions differ in their naturalness in the explicit ignorance context if their HDI does not include 0.

As shown in Table \ref{t:pairwise},\footnote{While the naturalness ratings collected from the participants range from 0 to 1, the greater than $|$1$|$  estimated marginal mean differences are the result of the beta regression using a logit link function for the mean parameter. The full model output is available here: \url{LINK TO TABLE IN REPO} {\bf ADD THIS AFTER FINALIZING SCRIPTS}.} the pairwise comparison suggests differences between the naturalness ratings of the CCs of the five factive predicates: The ratings of {\em be annoyed} are lower than those of {\em know}, which in turn are lower than those of {\em see} and {\em discover}, which in turn are lower than those of {\em reveal}. There is also variation between the factive predicates and the presuppositional controls: While all five factive predicates are more natural in explicit ignorance contexts than {\em continue, too} and {\em also}, {\em know} is additionally more natural than {\em again} and {\em stop}, and {\em see, discover} and {\em reveal} are additionally more natural than the {\em it-}cleft. Finally, the naturalness ratings in explicit ignorance contexts for {\em see} and {\em discover} do not differ from those of the nonfactives {\em confess, inform}, and {\em acknowledge}, and those of {\em reveal} do not differ from those of the nonfactives {\em admit, hear}, and {\em prove}. These results suggest that naturalness ratings in explicit ignorance contexts do not provide empirical support for categorical projection or for a categorical distinction between factive and nonfactive predicates.

\begin{table}[!h]
\addtolength{\tabcolsep}{-.19em}
\centering
\begin{tabular}{r | cccccccccccccccccccccccccc}
& \rots{\bf continue} & \rots{\bf too} & \rots{\bf also} & \rots{\bf again} & \rots{\bf stop} & \rots{\color{orange}{\bf be annoyed}\color{black}} & \rots{\bf cleft} & \rots{\color{orange}{\bf know}\color{black}} & \rots{\color{green}{\bf demonstrate}\color{black}} & \rots{\color{green}{\bf pretend}\color{black}} & \rots{\color{green}{\bf inform}\color{black}} & \rots{\color{green}{\bf confess}\color{black}} & \rots{\color{orange}{\bf see}\color{black}} & \rots{\color{green}{\bf acknowledge}\color{black}} & \rots{\color{orange}{\bf discover}\color{black}} & \rots{\color{green}{\bf admit}\color{black}} & \rots{\color{green}{\bf hear}\color{black}} & \rots{\color{green}{\bf prove}\color{black}} & \rots{\color{orange}{\bf reveal}\color{black}} & \rots{\color{green}{\bf announce}\color{black}} & \rots{\color{green}{\bf be right}\color{black}} & \rots{\color{green}{\bf establish}\color{black}} & \rots{\color{green}{\bf confirm}\color{black}} & \rots{\color{green}{\bf suggest}\color{black}} & \rots{\color{green}{\bf think}\color{black}} & \rots{\color{green}{\bf say}\color{black}} \\
\hline
\input{../../results/main/models/analysis1/table1}
\hline
\end{tabular}
\caption{Pairwise differences between expressions in the explicit ignorance context. The color coding indicates whether the difference between the means of row expressions and column expressions was positive or negative, as well as the size of the difference. A white cell means that the 95\% HDI included 0.\\
Positive difference: \colorbox{purple1}{\makebox[4em][c]{$>=1.5$}}, \colorbox{purple2}{\makebox[4em][c]{($1.5,0.5]$}}, 
\colorbox{purple3}{\makebox[4em][c]{($0.5, 0]$}} \\
Negative difference: \colorbox{yellow1}{\makebox[4em][c]{$>=-1.5$}}, \colorbox{yellow2}{\makebox[4em][c]{($-1.5, -0.5]$}}, \colorbox{yellow3}{\makebox[4em][c]{($-0.5, 0]$}} 
}\label{t:pairwise}
\end{table}

@@

These observations were confirmed by posthoc pairwise comparisons of the naturalness ratings in the three contexts for each of the 20 predicates, again using the `emmeans' package (\citealt{emmeans}). The input to the pairwise comparisons were 20 Bayesian mixed-effects beta regression models with weakly informative priors that were fitted using the `brms' package (\citealt{buerkner2017}). The models predicted, for each predicate, the naturalness ratings\footnote{As in the model reported above, the ratings were transformed to the interval (0,1).} from a fixed effect of context (with treatment coding and `explicit ignorance' as reference level) and included random by-item intercepts. The output of the pairwise comparison are 95\% HDIs of estimated marginal mean differences between each of the three contexts for each of the 20 contents. We assume that the naturalness ratings between two contexts differ if their HDI does not include 0.\footnote{The full model output is available here: \url{LINK TO TABLE IN REPO}.{\bf ADD AFTER FINALIZING SCRIPTS}} As shown in Fig.~\ref{fig:acc-by-context}, naturalness ratings in explicit ignorance vs.\ lower or higher prior probability contexts do not provide support for a categorical distinction between presuppositions and nonpresuppositions.
